---
title: "UMR Tribs nutrient conc vs. land use and litho"
author: "Lienne Sethna"
date: "June 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Multiple linear regression using Fixed_summarystats by Station. Comparing Si, TN, and TP average concentrations with land use and lithology by UMR trib LOCATCD.

parse out trib data from Fixed_summarystats:
```{r}
Fixed_summarystats=read.csv(file="Fixed_summarystats.csv", header=TRUE, sep=",")
Trib_nutrientavg = subset(Fixed_summarystats, Fixed_summarystats$dataset=="trib")
```

create dataframe of trib averages for Si, N, and P
```{r}
Trib_Siavg = subset(Trib_nutrientavg, Trib_nutrientavg$parameter=="SI")
Trib_Navg = subset(Trib_nutrientavg, Trib_nutrientavg$parameter=="TN")
Trib_Pavg = subset(Trib_nutrientavg, Trib_nutrientavg$parameter=="TP")

TribLOCAT_Si = data.frame(LOCATCD=Trib_Siavg$LOCATCD, Si_avg=Trib_Siavg$mean.val)
TribLOCAT_TN = data.frame(LOCATCD=Trib_Navg$LOCATCD, TN_avg=Trib_Navg$mean.val)
TribLOCAT_TP = data.frame(LOCATCD=Trib_Pavg$LOCATCD, TP_avg=Trib_Pavg$mean.val)
```

combine land use/litho data with nutrient averages
which LOCATCDs are missing?
```{r}
Trib_LULCLith_6.8.19 = read.csv(file="Trib_LULCLith_6.8.19.csv", header=TRUE, sep=",")
Trib_LOCATCD=data.frame(LOCATCD=unique(Trib_nutrientavg$LOCATCD))
setdiff(Trib_LOCATCD, Trib_LULCLith_6.8.19)
#Not sure how to code this, all 26 tribs return
```

```{r}
Trib_LULCLith_Siavg = merge(Trib_LULCLith_6.8.19, TribLOCAT_Si, by="LOCATCD")
Trib_LULCLith_TNavg = merge(Trib_LULCLith_6.8.19, TribLOCAT_TN, by="LOCATCD")
Trib_LULCLith_TPavg = merge(Trib_LULCLith_6.8.19, TribLOCAT_TP, by="LOCATCD")
```

multiple linear regression for LULC and lithology with average Si concentrations
create "forest" LU type as sum of Decid and MixedEvergreen
```{r}
Trib_LULCLith_Siavg$forested = Trib_LULCLith_Siavg$Decid+Trib_LULCLith_Siavg$MixedEvergreen
Trib_SiMLR = lm(Si_avg~Devl+CultCrops+forested+Dolostone+Sandstone, Trib_LULCLith_Siavg)
summary(Trib_SiMLR)
```
Land use is not a significant predictor of average Si concentrations
```{r}
Trib_LU.SiMLR = lm(Si_avg~Devl+CultCrops+forested,Trib_LULCLith_Siavg)
summary(Trib_LU.SiMLR)
```
Dolostone vs. Limestone is not a significant predictor of average Si concentrations
```{r}
Trib_litho.SiMLR = lm(Si_avg~Dolostone+Sandstone, Trib_LULCLith_Siavg)
summary(Trib_litho.SiMLR)
```

MLR for average TN and TP concentrations
```{r}
Trib_LULCLith_TNavg$forested = Trib_LULCLith_TNavg$Decid+Trib_LULCLith_TNavg$MixedEvergreen
Trib_LU.TNMLR = lm(TN_avg~Devl+CultCrops+forested,Trib_LULCLith_TNavg)
summary(Trib_LU.TNMLR)
Trib_litho.TNMLR = lm(TN_avg~Dolostone+Sandstone, Trib_LULCLith_TNavg)
summary(Trib_litho.TNMLR)

Trib_LULCLith_TPavg$forested = Trib_LULCLith_TPavg$Decid+Trib_LULCLith_TPavg$MixedEvergreen
Trib_LU.TPMLR = lm(TP_avg~Devl+CultCrops+forested,Trib_LULCLith_TPavg)
summary(Trib_LU.TPMLR)
Trib_litho.TPMLR = lm(TP_avg~Dolostone+Sandstone, Trib_LULCLith_TPavg)
summary(Trib_litho.TPMLR)
```