---
title: "UMR tribs spatial analysis"
author: "Lienne Sethna"
date: "July 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Merge tributary coordinates with Fixed summary stats for 2010-2018
```{r}
UMR_trib = merge(Fixed_summarystats_2010.2018, tribname_coordinates, by="LOCATCD")
```

Rank latitude values and compare with "relative downstream position"
Higher latitude values represent more northern (upstream) sites
```{r}
UMR_trib$lat.rank = rank(UMR_trib$Lat, ties.method = "min")
UMR_trib_lat_rank=data.frame("value"=unique(UMR_trib$lat.rank))
UMR_trib_lat_rank$rank=rank(UMR_trib_lat_rank$value)
UMR_trib$lat_rank=ifelse(UMR_trib$lat.rank==UMR_trib_lat_rank$value, UMR_trib_lat_rank$rank, "")

Trib_names_locations=Trib_names_locations[c("LOCATCD", "Relative Downstream Position")]
UMR_trib_locations=merge(UMR_trib, Trib_names_locations, by="LOCATCD")
plot(UMR_trib_locations$lat_rank, UMR_trib_locations$`Relative Downstream Position`)
```
Relative downstream position matches with latitudes

Get Si, Si:TN, and Si:TP parameters from fixed summary stats
Log transform ratios
```{r}
UMR_trib_Si = subset(UMR_trib, UMR_trib$parameter=="SI")
UMR_trib_SiTN = subset(UMR_trib, UMR_trib$parameter=="SiTN")
UMR_trib_SiTN$log.mean.val = log10(UMR_trib_SiTN$mean.val)
UMR_trib_SiTP = subset(UMR_trib, UMR_trib$parameter=="SiTP")
UMR_trib_SiTP$log.mean.val = log10(UMR_trib_SiTP$mean.val)
```

Plot Si, Si:TN, and Si:TP by latitude
```{r, echo=FALSE}
library(ggplot2)
library(grDevices)
UMR_trib_Sispatial = ggplot(UMR_trib_Si, aes(x=Lat, y=mean.val))+
  geom_point(size=3)+
  labs(title="UMR tributaries average Si concentration", y="Si concentration (mg SiO2/L)", x="Degrees latitude")+
  scale_x_reverse()
UMR_trib_Sispatial
ggsave(file="UMR_trib_Sispatial.png", width=10, height=7)
```
```{r, echo=FALSE}
UMR_trib_SiTNspatial = ggplot(UMR_trib_SiTN, aes(x=Lat, y=log.mean.val))+
  geom_point(size=3)+
  labs(title="UMR tributaries average Si:TN", y="log(Molar Si:TN)", x="Degrees latitude")+
  scale_x_reverse()
UMR_trib_SiTNspatial
ggsave(file="UMR_trib_SiTNspatial.png", width=10, height=7)
```
```{r echo=FALSE}
UMR_trib_SiTPspatial = ggplot(UMR_trib_SiTP, aes(x=Lat, y=log.mean.val))+
  geom_point(size=3)+
  labs(title="UMR tributaries average Si:TP", y="log(Molar Si:TP)", x="Degrees latitude")+
  scale_x_reverse()
UMR_trib_SiTPspatial
ggsave(file="UMR_trib_SiTPspatial.png", width=10, height=7)
```
Plot tributary Si, Si:TN, and Si:TP by FLDNUM
```{r, echo=FALSE}
UMR_trib_SiLM = UMR_trib_Si$mean.val ~ UMR_trib_Si$FLDNUM
UMR_trib_Si_FLDNUM = ggplot(UMR_trib_Si, aes(x=FLDNUM, y=mean.val))+
  geom_point(size=3)+
  labs(title="UMR tributaries average Si concentration and stoichiometry", y="[Si] (mg Si/L)", x="")+
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6"))+
  geom_smooth(method='lm', se=TRUE, color="black")+
  stat_poly_eq(formula=UMR_trib_SiLM, 
               aes(label=paste(..rr.label..)),
               label.x=0.85,
               size=8,
               parse = TRUE)+
  theme(text=element_text(size=20))+
  theme_bw()
UMR_trib_Si_FLDNUM

UMR_trib_SiTNLM = UMR_trib_SiTN$mean.val ~ UMR_trib_SiTN$FLDNUM
UMR_trib_SiTN_FLDNUM = ggplot(UMR_trib_SiTN, aes(x=FLDNUM, y=mean.val))+
  geom_point(size=3)+
  labs(y="Molar Si:TN", x="")+
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6"))+
  geom_smooth(method='lm', se=TRUE, color="black")+
  stat_poly_eq(formula=UMR_trib_SiTNLM, 
               aes(label=paste(..rr.label..)),
               label.x=0.85,
               size=8,
               parse = TRUE)+
  theme(text=element_text(size=50))+
  theme_bw()
UMR_trib_SiTN_FLDNUM

UMR_trib_SiTPLM = UMR_trib_SiTP$mean.val ~ UMR_trib_SiTP$FLDNUM
UMR_trib_SiTP_FLDNUM = ggplot(UMR_trib_SiTP, aes(x=FLDNUM, y=mean.val))+
  geom_point(size=3)+
  labs(y="Molar Si:TP", x="Field Number")+
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6"))+
  geom_smooth(method='lm', se=TRUE, color="black")+
  stat_poly_eq(formula=UMR_trib_SiTPLM, 
               aes(label=paste(..rr.label..)),
               label.x=0.85,
               size=8,
               parse = TRUE)+
  theme(text=element_text(size=30))+
  theme_bw()
UMR_trib_SiTP_FLDNUM

library(gridExtra)
grid.arrange(UMR_trib_Si_FLDNUM, UMR_trib_SiTN_FLDNUM, UMR_trib_SiTP_FLDNUM)
```
