---
title: "Woodstoich Si 2019"
output: html_document
---

```{r, echo=FALSE, include=FALSE}
library(readr)
library(ggplot2)
library(MASS)
library(car)
library(dplyr)
library(magrittr)
nla2012_waterchem_wide <- read_csv("C:/Users/pkthomas88/Box Sync/1. Woodstoich/nla2012_waterchem_wide.csv")

#removing zeros for microcystin:
nla2012_waterchem_wide_nozeros<-subset(nla2012_waterchem_wide, MICX_RESULT>0)

```


##*NOTE: I ran out of time to make the axes all pretty, but NTL_RESULT means total dissolved N concentration, PTL_RESULT means total dissolved P, etc and MICX_RESULT means concentration of microcystin somewhere in the lake. Also all of these stats were rushed through with no regard to statistical assumptions so should be taken with a grain of salt and just represent some quick exploratory stuff*

#PART 1 - Si stoichiometry and microcystin

## Distributions for silica, microcystin - both vary over several orders of magnitude, ~300 zeros removed for microcystin
```{r, echo=FALSE}

#summary(nla2012_waterchem_wide)

#log-transformed histogram with all Si data, shows that there is variation over a few orders of magnitude
ggplot(data=nla2012_waterchem_wide, aes(log(SILICA_RESULT)))+
  geom_histogram(binwidth = 1)


#histogram excluding values over 100
#shorter<-subset(nla2012_waterchem_wide, SILICA_RESULT<100)
#ggplot(data=shorter, aes(SILICA_RESULT))+
  #geom_histogram(binwidth = 1)

#ggplot(data=nla2012_waterchem_wide, aes(MICX_RESULT))+
 # geom_histogram(binwidth = 1)

ggplot(data=nla2012_waterchem_wide, aes(log(MICX_RESULT)))+
  geom_histogram(binwidth = 1)

#MICL and MICX have similar values
#ggplot(data=nla2012_waterchem_wide, mapping=aes(x=MICX_RESULT, y=MICL_RESULT))+
 # geom_smooth(method="lm")+geom_point()
```


##Si:P vs microcystin
```{r}

x<-ggplot(data=nla2012_waterchem_wide_nozeros, mapping=aes(x=log(SILICA_RESULT/PTL_RESULT), y=log(MICX_RESULT)))
x+geom_point()+geom_smooth(method="lm")+xlab("log(dissolved Si:P ratio)")+ylab("log(Microcystin concentration)")+theme_classic()

fit<-lm(data=nla2012_waterchem_wide_nozeros, log(MICX_RESULT)~log((SILICA_RESULT/PTL_RESULT)))
summary(fit)



```


##Si:N vs. microcystin
```{r}

x<-ggplot(data=nla2012_waterchem_wide_nozeros, mapping=aes(x=log(SILICA_RESULT/NTL_RESULT), y=log(MICX_RESULT)))
x+geom_point()+geom_smooth(method="lm")+xlab("log(dissolved Si:N ratio)")+ylab("log(Microcystin concentration)")+theme_classic()

fit<-lm(data=nla2012_waterchem_wide_nozeros, log(MICX_RESULT)~log((SILICA_RESULT/NTL_RESULT)))
summary(fit)
```


##Si:N and Si:P both explain microcystin in complementary ways accoriding to partial regression plots. Also both Si:N and Si:P are retained in the model

```{r}
fit<-lm(data=nla2012_waterchem_wide_nozeros, log(MICX_RESULT)~log(SILICA_RESULT/NTL_RESULT)+log((SILICA_RESULT/PTL_RESULT)))
summary(fit)
stepAIC(fit)
avPlots(fit)

```

## Same as above but just Si N P concentrations instead of ratios. This suggests that only N concentrations have an effect

```{r}
fit<-lm(data=nla2012_waterchem_wide_nozeros, log(MICX_RESULT)~log(SILICA_RESULT)+log(PTL_RESULT)+log(NTL_RESULT))
summary(fit)

stepAIC(fit)
avPlots(fit)

```

##N:P ratio doesn't explain much

```{r}
x<-ggplot(data=nla2012_waterchem_wide_nozeros, mapping=aes(x=log(NTL_RESULT/PTL_RESULT), y=log(MICX_RESULT)))
x+geom_point()+geom_smooth(method="lm")


#fit<-lm(data=nla2012_waterchem_wide, log(MICX_RESULT)~log((NTL_RESULT/PTL_RESULT)))
#summary(fit)
```



##trying to throw Si:N, Si:P, and N:P in one model totally fails, probably for obvious reasons that I haven't figured out yet
```{r}
fit<-lm(data=nla2012_waterchem_wide_nozeros, log(MICX_RESULT)~log(NTL_RESULT/PTL_RESULT)+log(SILICA_RESULT/PTL_RESULT)+log(SILICA_RESULT/NTL_RESULT))
summary(fit)
stepAIC(fit)
avPlots(fit)
```


#PART 2 - Si:N, Si:P, N:P and community composition
```{r}
nla2012_wide_phytoplankton_count_02122014 <- read_csv("C:/Users/pkthomas88/Box Sync/1. Woodstoich/nla2012_wide_phytoplankton_count_02122014.csv")

nla2012_chem_phyto_joined<-full_join(nla2012_wide_phytoplankton_count_02122014, nla2012_waterchem_wide_nozeros, by="UID")


cyanos<-subset(nla2012_chem_phyto_joined, ALGAL_GROUP=="BLUE-GREEN ALGAE")
diatoms<-subset(nla2012_chem_phyto_joined, ALGAL_GROUP=="DIATOM")

```



```{R, include=FALSE, echo=FALSE}

#Si stoich vs cyanobacteria total abundance
group_by(cyanos, UID) %>% summarize(cyanototabundance=sum(ABUNDANCE)) -> poop
nla2012_cyanos<-full_join(nla2012_waterchem_wide_nozeros,poop, by="UID")

ggplot(data=nla2012_cyanos, mapping = aes(x=log(SILICA_RESULT/PTL_RESULT), y=log(cyanototabundance)))+
  geom_point()+geom_smooth(method = "lm")

ggplot(data=nla2012_cyanos, mapping = aes(x=log(SILICA_RESULT/NTL_RESULT), y=log(cyanototabundance)))+
  geom_point()+geom_smooth(method = "lm")

ggplot(data=nla2012_cyanos, mapping = aes(x=log(NTL_RESULT/PTL_RESULT), y=log(cyanototabundance)))+
  geom_point()+geom_smooth(method = "lm")
```


##Si stoich vs cyanobacteria total biovolume
```{R}

group_by(cyanos, UID) %>% summarize(cyanototbiovolume=sum(BIOVOLUME)) -> poop
nla2012_cyanos<-full_join(nla2012_waterchem_wide_nozeros,poop, by="UID")

ggplot(data=nla2012_cyanos, mapping = aes(x=log(SILICA_RESULT/PTL_RESULT), y=log(cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_cyanos, log(cyanototbiovolume)~log(SILICA_RESULT/PTL_RESULT))
summary(fit)

ggplot(data=nla2012_cyanos, mapping = aes(x=log(SILICA_RESULT/NTL_RESULT), y=log(cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_cyanos, log(cyanototbiovolume)~log(SILICA_RESULT/NTL_RESULT))
summary(fit)

ggplot(data=nla2012_cyanos, mapping = aes(x=log(NTL_RESULT/PTL_RESULT), y=log(cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_cyanos, log(cyanototbiovolume)~log(NTL_RESULT/PTL_RESULT))
summary(fit)


```

##Unlike the above microcystin data, only Si:P has an effect on cyanobacteria biovolume when it's put in a model with Si:N. hmm. 

```{R}

fit<-lm(data=nla2012_cyanos, log(cyanototbiovolume)~ log(SILICA_RESULT/PTL_RESULT)+ log(SILICA_RESULT/NTL_RESULT))
summary(fit)
avPlots(fit)

```

##Si stoich vs diatom total biovolume

```{r}

group_by(diatoms, UID) %>% summarize(diatomtotbiovolume=sum(BIOVOLUME)) -> poop
nla2012_diatoms<-full_join(nla2012_cyanos,poop, by="UID")

ggplot(data=nla2012_diatoms, mapping = aes(x=log(SILICA_RESULT/PTL_RESULT), y=log(diatomtotbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume)~log(SILICA_RESULT/PTL_RESULT))
summary(fit)


ggplot(data=nla2012_diatoms, mapping = aes(x=log(SILICA_RESULT/NTL_RESULT), y=log(diatomtotbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume)~log(SILICA_RESULT/NTL_RESULT))
summary(fit)


ggplot(data=nla2012_diatoms, mapping = aes(x=log(NTL_RESULT/PTL_RESULT), y=log(diatomtotbiovolume)))+
  geom_point()+geom_smooth(method = "lm")
fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume)~log(NTL_RESULT/PTL_RESULT))
summary(fit)

#mutate(nla2012_diatoms, dia.cyano=diatomtotbiovolume/cyanototbiovolume)

```


##Effects of Si:P etc on ratio of diatoms:cyanobacteria. Not sure what to make of this, but I guess high Si:N and high Si:P both explain the community ratio, however when you put them both in a model only Si:N has an effect. Also total Si concentration has a weaker effect than the ratios

```{R}

ggplot(data=nla2012_diatoms, mapping = aes(x=log(SILICA_RESULT/PTL_RESULT), y=log(diatomtotbiovolume/cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")+
  xlab("log(dissolved Si:P ratio)")+
  ylab("log(Diatom:Cyano biovolume ratio)")

fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume/cyanototbiovolume)~log(SILICA_RESULT/PTL_RESULT))
summary(fit)

ggplot(data=nla2012_diatoms, mapping = aes(x=log(SILICA_RESULT/NTL_RESULT), y=log(diatomtotbiovolume/cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")+
  xlab("log(dissolved Si:N ratio)")+
  ylab("log(Diatom:Cyano biovolume ratio)")

fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume/cyanototbiovolume)~log(SILICA_RESULT/PTL_RESULT)+log(SILICA_RESULT/NTL_RESULT))
summary(fit)
avPlots(fit)

ggplot(data=nla2012_diatoms, mapping = aes(x=log(SILICA_RESULT), y=log(diatomtotbiovolume/cyanototbiovolume)))+
  geom_point()+geom_smooth(method = "lm")

fit<-lm(data=nla2012_diatoms, log(diatomtotbiovolume/cyanototbiovolume)~log(SILICA_RESULT))
summary(fit)
```


#PART 3 - Effects of Si:P on zooplankton production

##Worth checking if dissolved Si:P and Si:N have any effects on trophic transfer to zooplankton? Si should make for harder to eat diatom prey, P is often limiting for zooplankton, so maybe that combo would make for stronger effects?


```{r}

```

```{r}

```

